---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

###read activity.csv

```{r temp,echo=TRUE}
activity = read.csv('activity.csv')
```

###show details 

```{r temp2,echo=TRUE}
print(head(activity))
print(summary(activity))
print(str(activity))
```



## What is mean total number of steps taken per day?

###Calculate the total number of steps taken per day 

```{r temp3,echo=TRUE}
library(dplyr)
library(ggplot2)
sub_activity = subset(activity,!is.na(steps),select = c(steps,date))
STPD = summarise(group_by(sub_activity,date),steps = sum(steps))
print(STPD)
qplot(steps,data = STPD)
```
### figure1

###Calculate the mean & median number of steps taken per day 

```{r temp4,echo=TRUE}
sub_M_activity = subset(activity,!is.na(steps),select = c(steps,date))
STPD = summarise(group_by(sub_activity,date),steps = sum(steps))
print (mean(STPD$steps))
print (median(STPD$steps))
```

## What is the average daily activity pattern?

```{r temp5,echo=TRUE}
sub_interval_activity = subset(activity,!is.na(steps),select = c(steps,interval))
STI = summarise(group_by(sub_interval_activity,interval),steps = mean(steps))
qplot(interval,steps,data = STI,type = '1')
```
### figure2
```{r tempx,echo=TRUE}
ggplot(STI, aes(interval, steps)) + geom_line()
```
### figure3
```{r tempy,echo=TRUE}
STI[STI$steps == max(STI$steps),]
```



## Imputing missing values
###Calculate and report the total number of missing values in the dataset 
```{r temp6,echo=TRUE}
library(dplyr)
library(ggplot2)
sub_activity = subset(activity,is.na(steps),select = c(steps,date))
print(length(sub_activity$steps))
```
### NA values change to main

```{r temp7,echo=TRUE}
data = read.csv('activity.csv')
sub_activity = subset(data,!is.na(steps),select = c(steps,date))
data$steps[is.na(data$steps)] = mean(sub_activity$steps)
STPD = summarise(group_by(data,date),steps = sum(steps))
print(STPD)
qplot(steps,data = STPD)
```
### figure4

## Are there differences in activity patterns between weekdays and weekends?

```{r temp8,echo=TRUE}
data = read.csv('activity.csv')
weekdays = weekdays(as.Date(data$date))
i = 1 
weekend = c()
for(day in weekdays){
    if(day == "Sunday"){
        weekend[i] = TRUE
    }
    else{
        weekend[i] = FALSE
    }
    i = i + 1
}
days =data.frame(weekdays,weekend)
data = cbind(data,days)
sub_activity = subset(data,!is.na(steps),select = c(steps,date))
STPD = summarise(group_by(sub_activity,date),steps = sum(steps))
qplot(x = interval,	y = steps,	data = data,color = factor(weekend))	
```
### figure5
